\begin{abstract}
	This is abstract.
\end{abstract}

\section{Introduction}
Cosmic rays physics as a frontier to discover and validate laws of physics has existed for quite some time. As early as 1912, Victor Hess already used balloon with "electrometers" to detect ionizing radiation at an altitude~\cite{wiki:cosmic}. Nowadays, cosmic rays is a popular research area with numerous large scale experiments, such as IceCube, AMS-02, and Pierre Auger. Although cosmic rays experiments suffer from uncontrolled particles sources, its energy (up to \SI{1e20}{\eV}) exceed state-of-art accelerator energy (up to \SI{13}{\tera\eV}) by a large margin~\cite{Gaisser}. 

A large portion of cosmic rays consists of neutrinos, which have a tons of unsolved mysteries, like neutrino oscillations, origin of its mass and $\mathcal{CP}$ (even $\mathcal{CPT}$ violation~\cite{Barenboim_2017}) violations. By studying energy spectrum of comic rays, we can look into the propagation of these particles and thus determine properties of intergalactic space~\cite{Gaisser}. Sometimes features of cosmic rays might need dark matter to make sense~\cite{grupen}\cite{Gomez_Coral_2020}.

Beside all these potential intriguing problem, the setup of Styx has a rich heritage. The straw modules were formerly a part of ZEUS Straw Tube Tracker (STT) to study secondary cosmic rays~\cite{Styx}.

This report is arranged as following. A general overview of cosmic rays is given in section~\ref{sec:theo}. Electronics and schematics of the setup are shortly introduced in section~\ref{sec:setup}. Before the data taking, optimal operating voltage PMT and threshold of discriminators need to be set and straws should be calibration. These are done in sections~\ref{sec:vol} and section~\ref{sec:cal}. The tracking analysis is presented in section~\ref{sec:ana}. Section~\ref{sec:con} concludes this report.
